|

### 2022-11-16 manuscript.Rmd
change acm to american computing machinery

According to LinkedIn's U.S. Emerging Jobs Report, data scientists rank among the top emerging jobs [-@linkedin]. With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula. However, a consensus on what should be included in such curricula has not yet been reached. One of the few guidelines on the topic is written by the ACM Data Science Task Force and titled *Computing Competencies for Undergraduate Data Science Curricula*. In this report, accessibility is a "foundational consideration" at the knowledge level when it comes to displaying data [@danyluk2021computing].

>>>>

According to LinkedIn's U.S. Emerging Jobs Report, data scientists rank among the top emerging jobs [-@linkedin]. With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula. However, a consensus on what should be included in such curricula has not yet been reached. One of the few guidelines on the topic is written by the American Computing Machinery Data Science Task Force and titled *Computing Competencies for Undergraduate Data Science Curricula*. In this report, accessibility is a "foundational consideration" at the knowledge level when it comes to displaying data [@danyluk2021computing].
